Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-02-13 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
yny

The value of $\beta$ can be estimated by first
converting the apparent permeability of a 
bilayer~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
conductivity $k_w$ using the conversion
in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native membrane permeability for water is $10^{-11}\le
\beta\le 10^{-9}$. 
%
In our simulations the equilibrium shape of a semipermeable membrane in open space is found to be independent of $\beta$ for $10^{-5}\le\beta\le10^{-2}$.
Within this range we find that the permeability $\beta$ only affects the time it takes to reach the equilibrium membrane shape, which is determined by the background flow
(such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.)
From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable inextensible membrane 
with a smaller $\beta$ ($\beta\ne 0$). 
On the other hand,  when $\beta\ge 0.1$, we find that the membrane shape swells to maximize the water content inside the membrane, independent of the initial reduced 
area and the imposed flow in the far field.
In the simulations we focus on intermediate value of $10^{-5}\le \beta\le 10^{-3}$ to investigate the hydrodynamics of a semipermeable inextensible membrane. 
%
Under strong confinement, $10^{-4}\le\beta\le10^{-3}$ is needed in our
simulations to keep the membrane tension below the threshold value for
membrane poration $\sim 10^{-3}$ N/m. Such range of $\beta$ may imply
that the lipid bilayer membrane would be porated under large stress
caused by confinement.

\subsection{Dynamics of Vesicle Area\label{subsec:area_dynamics}}
In the absence of an imposed flow, the steady state vesicle shape and a
differential equation for the area of the vesicle can be derived. We
start by following the analysis of Veerapaneni {\em et
al.}~\cite{vee-raj-bir-pur2009} by computing the steady state shape of a
semipermeable vesicle in a quiescent flow. The steady state shape is a
stationary point of the Lagrangian
\begin{align}
  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
    \Lambda \left(\int_{\gamma} ds  - L \right),
\end{align}
where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
of the pressure Lagrange multiplier since the total water content inside the vesicle membrane is not conserved.
Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
setting it to zero, the steady state shape satisfies $\kappa_{ss} +
\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Multiplying by $\kappa_s$
and integrating once, we have
\begin{align}
  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
    \frac{\Lambda}{2}\kappa_0^2.
  \label{eqn:curveODE}
\end{align}
Assuming $\kappa_s \neq 0$, Equation~\eqref{eqn:curveODE} is separable,
and can be solved analytically in terms of the {\em EllipticF} function
using Mathematica. Unlike in the impermeable case, the solution of
Equation~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) =
\kappa_0$. Therefore, the equilibrium shape of a semipermeable vesicle
in a quiescent flow is a circle with radius $L/2\pi$ and constant
tension $\Lambda = \kappa^2/2 = 2\pi^2/L^2.$ Note that in contrast to a
impermeable vesicle, the steady state tension is positive rather than
negative. Such equilibrium shape of a semipermeable vesicle results from
the balance between elastic stress and membrane tension. For an elastic
membrane with a large pore, the equilibrium membrane (hemispherical)
shape also results from such a balance~\cite{Ryham2018_JFM}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a) Snapshots of four
  semipermeable vesicles with $\beta = 10^{-8}$ submerged in a fluid
  with no background flow. Time goes from left to right. The red regions
  correspond to influx and the blue regions correspond to efflux. In all
  cases, the vesicle reaches a steady state circular shape. (b) The
  reduced area of each of the simulations. The particular snapshots in
  (a) occur at the marks along the curve.}
\end{figure*}
The analysis in \S~\ref{subsec:area_dynamics} shows
that a semipermeable inextensible membrane relaxes to a circle at a rate that is
proportional to $\beta$, regardless of the initial membrane shape (for a fixed length):
In the absence of a background flow, a semipermeable inextensible membrane in free
space is quantified in terms of its area dynamics and transition
to the equilibrium shape, which is a circular membrane with a uniform 
membrane tension $\Lambda = 2\pi^2/L^2$.
This is in stark contrast with the impermeable vesicle relaxing to equilibrium that depends on the vesicle reduced area,  which remains constant for $\beta=0$.
%
Our analysis further shows that the rate of change in area enclosed inside a
semipermeable inextensible membrane is proportional to $\beta$. For this reason,
our numerical results are reported in terms of the scaled time $\beta t$.

In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
dynamics of a semipermeable vesicle with four initial shapes and reduced
areas as labeled. The vesicles on the left are color-coded by the water
permeation flux: red denotes an influx into the vesicle, and blue
denotes an efflux out of the vesicle. First we observe that the initial
vesicle shape determines the direction of water flux. For the vesicle
with an initial reduced area $\alpha(0)=0.12$ (bottom row) the vesicle
deflates (blue regions) first due to the high interior capillary
pressure that corresponds to the high membrane curvatures. For the other
three cases efflux is dominated by influx, especially after $t=1$ day
when the increase in total water content becomes non-negligible.
%
%is found at some locations of high curvature, while
%mostly water permeates into the vesicle and significant change in the
%reduced area is found at $t\sim 1$ hour. 
%
Over time (about four weeks) all vesicles inflate and as expected, each
vesicle eventually reaches a circular shape with reduced area
$\alpha=1$. 
%%These regions are denoted in blue and are only present at early times. 
%Finally, the vesicles's reduced area do not steady state tension is
%$\Lambda = 2\pi^2/L^2$. 
%Therefore, the times for the vesicle to deviate from its initial reduced area and to reach its
%steady state are proportional to $\beta^{-1}$. 
%
%Each of the four cases in Figure~\ref{fig:relaxationComposite} eventually
%reaches a circular shape with reduced area $\alpha=1$. Next, we observe
%that even though the vesicle is inflating to a circle, 
%%meaning that there is a net flux into the vesicle, 
%there are regions where the flux
%is out of the vesicle. These regions are denoted in blue and are only
%present at early times. 
%
%Finally, the vesicles's reduced area do not
%change by much at early times (up to ten minutes), and

Between $t=30$ minutes and $t=1$ day, the total water content is nearly constant.
%
%the intermediate shapes of
%semipermeable vesicles resemble the shape of an impermeable vesicle.
%
This can be explained by considering the two terms that contribute to
the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
\nn) \nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since
$\beta\ll 1$, the permeability velocity is much smaller than the force
balance velocity at early times, and the semipermeable vesicle dynamics
resemble those of an impermeable vesicle. As the force balance velocity
decreases, the permeability velocity dominates, and the vesicle begins
to inflate to a circle with vanishing force and velocity.

\begin{figure*}[htp]
  \centering
  \ifTikz
    \input{figures/relaxationTensions.tikz}
  \else
    \includegraphics{figures/relaxationTensions.pdf}
  \fi
  \caption{\label{fig:relaxationTensions} The distribution of membrane
  tension of a relaxing vesicle that corresponds to
  Figure~\ref{fig:relaxationComposite}.}
\end{figure*}
Figure~\ref{fig:relaxationTensions} shows the membrane tension
distribution along the relaxing vesicles in
Figure~\ref{fig:relaxationComposite}. The membrane tension (color bars)
is in N/m. As the semipermeable vesicle relaxes, the membrane tension
reduces in magnitude and becomes more evenly distributed along the
membrane. In the top row ($\alpha(0)=0.95$) the vesicle nearly relaxes
to a circle on the right, and the membrane tension is uniform and equal
to $k_b \kappa_0^2/2$ as predicted by our analysis in
Equation~\eqref{eqn:areaROC2}. 
%In the bottom row ($\alpha(0)=0.12$), the initial vesicle shape has a
%lot of high curvature regions (and thus the low reduced area), and it
%takes more than four hours to inflate to twice the initial total water
%content for $\beta=10^{-7}$. In contrast the water enclosed inside the
%vesicle in the top row remains nearly constant in the first four hours.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Planar Shear Flow}
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \else
  \includegraphics{figures/shearComposite.pdf}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semipermeable vesicle with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The equilibrium shape of a vesicle with varying flow rates and
  membrane permeability. The red regions correspond to influx and the
  blue regions correspond to efflux The boxed vesicles correspond to the
  simulation results in part (a).}
\end{figure*}

We consider a semipermeable vesicle in a planar shear flow,
characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
%in the non-dimensionalization 
(see \S~\ref{sec:formulation}) and $\chi$ is the shear rate of the
planar shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
(impermeable case), the vesicle reduced area and fluid viscosity
contrast determine whether a vesicle tank treads or
tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
semipermeable vesicles with no viscosity contrast, we find that a
semipermeable vesicle tilts to an inclination angle and undergoes
tank-treading dynamics, similar to the case of an impermeable vesicle.

In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
and two flow rates, we plot the reduced area of a semipermeable vesicle
with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
vesicle shape is independent of the initial reduced area. However, it
does depend on the flow rate. We also observe that the amount of water
inside the vesicle remains constant until $t\sim 2$ hours, when the
normal component of the flow velocity becomes significantly smaller than
the permeable velocity, leading to a changing reduced area.

For a range of dimensionless permeability coefficient $\beta>0$ and
capillary number $Ca_\mathrm{E}$, a semipermeable vesicle reaches an
equilibrium shape as in Figure~\ref{fig:shearComposite}(a). Since the
equilibrium shape depends on $Ca_\mathrm{E}$ and is independent of the
initial reduced area, we initialize the vesicle with reduced area
$\alpha = 0.65$ for all simulations in
Figure~\ref{fig:shearComposite}(b), where we summarize the equilibrium
vesicle shape and its reduced area. We see that the capillary number
(flow rate) significantly affects the final vesicle shape, but the
permeability coefficient has a very minor effect on the equilibrium
shape for $10^{-4}\le\beta\le 10^{-2}$. Instead, $\beta$ sets the time
required for a vesicle to reach its steady state configuration which is
proportional to $\beta^{-1}$, as we saw in the analysis for the
quiescent flow (\S~\ref{subsec:area_dynamics}).

%Our simulations of a semipermeable vesicle in a planar shear flow show
%that the equilibrium vesicle shape depends mostly on the capillary
%number $Ca_\mathrm{E}$, independent of the dimensionless water
%permeability $\beta$. 
The tension distribution along the equilibrium vesicle at
$\beta=10^{-4}$ is shown in Figure~\ref{fig:shearTensions}, where the
color bars are the membrane tension in N/m. The capillary number
$Ca_\mathrm{E}$ increases from Figures~\ref{fig:shearTensions}(a)--(d),
and we observe that the tension magnitude also increases almost linearly
with $Ca_\mathrm{E}$. We also observe that the membrane tension is
relatively small at the tip when the membrane curvature is large due to
the extensional component in the shear flow.
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/shearTensions.tikz}
  \else
  \includegraphics{figures/shearTensions.pdf}
  \fi
  \caption{\label{fig:shearTensions} The tension distribution along a
  vesicle in a linear shear flow. The semipermeability constant is
  $\beta = 10^{-4}$ for all these cases, and the elastic capillary
  numbers are (a) $10^{-1}$, (b) $10^{0}$, (c), $10^{1}$, and (d)
  $10^{2}$ as in Figure~\ref{fig:shearComposite}(b).}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Poiseuille Flow}
We consider a semipermeable vesicle in the Poiseuille flow $\uu =
U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
non-linear effects of the Poiseuille flow on the migration of an
impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At a
given value of the maximum velocity $U$, there exists a critical reduced
volume above which the equilibrium vesicle shape is symmetric (parachute
or bullet shapes) and the vesicle stays at $y=0$. Below this critical
reduced volume the equilibrium vesicle moves off the center and is
asymmetric (tank-treading slipper shape). We validated our numerical
codes by comparing against results in~\citet{kao-bir-mis2009} (see
\S~\ref{subsec:numerical_validation}).

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicComposite.tikz}
  \else
  \includegraphics{figures/parabolicComposite.pdf}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The equilibrium shape of
  a semipermeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. The red regions correspond to
  influx and the blue regions correspond to efflux. (b) The steady
  state vertical displacement at four different flow velocities. The
  steady state shapes are superimposed. (c) The reduced area of the
  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The vesicle
  shape shown with the background imposed flow. The channel width is
  12.5 times larger than the vesicle radius. The corresponding reduced
  area of each vesicle is indicated by the marks in plot (c).}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicTensions.tikz}
  \else
  \includegraphics{figures/parabolicTensions.pdf}
  \fi
%  \begin{tikzpicture}[scale=1]
%    \node[inner sep=0pt] at (0,0) {
%    \includegraphics[width=\textwidth]{figures/parabolicTensions.pdf}
%    };
%    \node at (-8.2,1.5) {(a)};
%    \node at (-3.8,1.5) {(b)};
%    \node at (+0.6,1.5) {(c)};
%    \node at (+5.0,1.5) {(d)};
%  \end{tikzpicture}
  \caption{\label{fig:parabolicTensions} The equilibrium tension
  distribution of a semipermeable vesicle with $\beta=10^{-3}$ in a
  parabolic flow (Figure~\ref{fig:parabolicComposite}). The flow
  velocities are (a) 200 $\mu$m/s, (b) 400 $\mu$m/s, (c) 600 $\mu$m/s,
  and (d) 800 $\mu$m/s.}
\end{figure*}
 The membrane tension distribution of the equilibrium shapes are shown
 in Figure~\ref{fig:parabolicTensions} for the flow velocities $U$ from
 $200\;\mu$m/s to $800 \;\mu$m/s. We note that in the Poiseuille flow
 the membrane tension is positive in the front, and negative in the rear
 part of the vesicle. Furthermore we also note that the tension
 magnitude is almost linearly proportional to $U$ as in the linear shear
 flow.

@@

\section{A semipermeable vesicle under strong confinement\label{sec:confinement}}
Here we consider a semipermeable vesicle under strong confinement: a
long closely-fit channel and a contracting channel. In a narrow
microfluidic channel, a large pressure jump is often needed to push the
vesicle through a closely-fit channel~\cite{abk-fai-sto2006}. Our
simulations show that such a configuration can lead to an amplification
of water permeation at a time scale shorter than a few minutes. In
addition, we find that a large value of $\beta$ is needed to keep the
membrane tension below the threshold value for membrane poration. Such
high permeability for water may be regarded as an indication that the
lipid bilayer membrane is porated under strong confinement, and our
model vesicle is for a porated vesicle within the Helfrich free energy
framework. As in the previous examples, we fix the vesicle length and
examine the enclosed water content as a dynamic consequence of water
flow, vesicle shape deformation, and membrane tension distribution.

>>>>

The value of $\beta$ can be estimated by first
converting the apparent permeability of a 
membrane~\cite{OlbrichRawiczNeedhamEtAl2000_BJ} to the hydraulic
conductivity $k_w$ using the conversion
in~\citet{FettiplaceHaydon1980_PhysRev}, and then scaling $k_w$ to $R_0/\mu$. We found that for most lipid bilayer membranes, $10^{-14}\le
k_w\le 10^{-12}$ m$^2$s/kg, thus the range of $\beta$ corresponding to the native water permeability of a lipid bilayer membrane (vesicle) is $10^{-11}\le
\beta\le 10^{-9}$, consistent with the value in \citet{vogl2014effect}. In the following we use a wider range of $\beta$ to elucidate the effects of permeating water flow across a
semipermeable inextensible membrane.
%

For example, we use $10^{-5}\le\beta\le10^{-2}$
in our simulations of a semipermeable inextensible membrane in free space under various flowing conditions.
We found that 
the equilibrium shape of a semipermeable membrane in free space to be independent of $\beta$.
Within this range of $\beta$ we find that $\beta$ only affects the time it takes for the membrane to reach the equilibrium shape, which is determined by the background flow
(such as a quiescent flow, a linear shear flow and its shear rate, and a Poiseuille flow and its maximum velocity.)
From these results and our analysis of area dynamics, we suspect similar hydrodynamics of a semipermeable vesicle
(with $10^{-11}\le\beta\le 10^{-9}$). 
%
When we use $\beta\ge 0.1$, we find that the semipermeable membrane swells to maximize its water content, independent of the initial reduced 
area and the background flow.
%
%In the simulations we focus on intermediate value of $10^{-5}\le \beta\le 10^{-3}$ to investigate the hydrodynamics of a semipermeable inextensible membrane. 
%

On the other hand,
under strong confinement,  we find that $10^{-4}\le\beta\le10^{-3}$ is needed in our
simulations to keep the membrane tension below the threshold value $\sim 10^{-3}$ N/m for
poration in a lipid bilayer membrane. Such range of $\beta$ may imply
that a vesicle would be porated under large stress
caused by confinement.

\subsection{Equilibrium and Areal Dynamics in a Quiescent Flow\label{subsec:area_dynamics}}
In the absence of an imposed flow, the steady equilibrium shape and a
differential equation for the area inside the semipermeable inextensible membrane can be derived
by following the analysis of Veerapaneni {\em et al.}~\cite{vee-raj-bir-pur2009} in a quiescent flow $({\bf u}_{\infty} = 0)$.
%
%by computing the steady state shape of a
%semipermeable vesicle in a quiescent flow. 
%
The steady state shape is a
fixed point of the Lagrangian
\begin{align}
  \mathcal{L} = \frac{1}{2}\int_{\gamma} \kappa^2 \, ds +
    \Lambda \left(\int_{\gamma} ds  - L \right),
\end{align}
where the Lagrange multiplier $\Lambda$ is the tension. Note the absence
of the pressure Lagrange multiplier since the total water content inside the vesicle membrane is not conserved.
Taking the variation of $\mathcal{L}$ with respect to $\gamma$ and
setting it to zero, the steady state shape satisfies $\kappa_{ss} +
\frac{1}{2}\kappa^3 - \Lambda \kappa = 0$, with initial conditions
$\kappa(0) = \kappa_0$ and $\kappa_s(0) = 0$.  Multiplying by $\kappa_s$
and integrating once, we have
\begin{align}
  \frac{\kappa_s^2}{2} + \frac{\kappa^4}{8} - 
    \frac{\Lambda}{2}\kappa^2 = \frac{\kappa_0^4}{8} - 
    \frac{\Lambda}{2}\kappa_0^2.
  \label{eqn:curveODE}
\end{align}
Assuming $\kappa_s \neq 0$, Equation~\eqref{eqn:curveODE} is separable,
and can be solved analytically in terms of the {\em EllipticF} function
using Mathematica. Unlike in the impermeable case, the solution of
Equation~\eqref{eqn:curveODE} is not periodic unless $\kappa(s) =
\kappa_0$. Therefore, the equilibrium shape of a semipermeable vesicle
in a quiescent flow is a circle with radius $L/2\pi$ and constant
tension $\Lambda = \kappa^2/2 = 2\pi^2/L^2.$ Note that in contrast to a
impermeable vesicle, the steady state tension is positive rather than
negative. Such equilibrium shape of a semipermeable vesicle results from
the balance between elastic stress and membrane tension. For an elastic
membrane with a large pore, the equilibrium membrane (hemispherical)
shape also results from such a balance~\cite{Ryham2018_JFM}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a) Snapshots of four
  semipermeable inextensible membranes with $\beta = 10^{-8}$ submerged in a fluid
  with no background flow. Time goes from left to right. The red regions
  correspond to influx and the blue regions correspond to efflux. In all
  cases, the vesicle reaches a steady state circular shape. (b) The
  reduced area of each of the simulations. The particular snapshots in
  (a) occur at the marks along the curve.}
\end{figure*}
The analysis in \S~\ref{subsec:area_dynamics} shows
that a semipermeable inextensible membrane relaxes to a circle at a rate that is
proportional to $\beta$, regardless of the initial membrane shape (for a fixed length):
In the absence of a background flow, a semipermeable inextensible membrane in free
space is quantified in terms of its area dynamics and transition
to the equilibrium shape, which is a circular membrane with a uniform 
membrane tension $\Lambda = 2\pi^2/L^2$.
This is in stark contrast with the impermeable vesicle relaxing to equilibrium that depends on the vesicle reduced area,  which remains constant for $\beta=0$.
%
Our analysis further shows that the rate of change in area enclosed inside a
semipermeable inextensible membrane is proportional to $\beta$. For this reason,
our numerical results are reported in terms of the scaled time $\beta t$.

In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
dynamics with four initial shapes and reduced
areas as labeled. The membrane shapes on the left are color-coded by the water
permeation flux: red denotes an influx into the membrane, and blue
denotes an efflux out of the membrane. First we observe that the initial
membrane shape determines the direction of water flux. For the case
with an initial reduced area $\alpha(0)=0.12$ (bottom row) the membrane
deflates (blue regions) first due to the high interior capillary
pressure that corresponds to the high membrane curvatures. For the other
three cases efflux is dominated by influx, especially after $t=1$ day
when the increase in total water content becomes non-negligible.
%
%is found at some locations of high curvature, while
%mostly water permeates into the vesicle and significant change in the
%reduced area is found at $t\sim 1$ hour. 
%
Over time (about four weeks) all cases inflate and as expected, each
case eventually reaches a circular shape with reduced area
$\alpha=1$. 
%%These regions are denoted in blue and are only present at early times. 
%Finally, the vesicles's reduced area do not steady state tension is
%$\Lambda = 2\pi^2/L^2$. 
%Therefore, the times for the vesicle to deviate from its initial reduced area and to reach its
%steady state are proportional to $\beta^{-1}$. 
%
%Each of the four cases in Figure~\ref{fig:relaxationComposite} eventually
%reaches a circular shape with reduced area $\alpha=1$. Next, we observe
%that even though the vesicle is inflating to a circle, 
%%meaning that there is a net flux into the vesicle, 
%there are regions where the flux
%is out of the vesicle. These regions are denoted in blue and are only
%present at early times. 
%
%Finally, the vesicles's reduced area do not
%change by much at early times (up to ten minutes), and

Between $t=30$ minutes and $t=1$ day, the total water content is nearly constant.
%
%the intermediate shapes of
%semipermeable vesicles resemble the shape of an impermeable vesicle.
%
This can be explained by considering the two terms that contribute to
the vesicle velocity: (i) the permeability velocity, $\beta(\ff \cdot
\nn) \nn$, and (ii) the force balance velocity, $\SS[\ff]$. Since
$\beta\ll 1$, the permeability velocity is much smaller than the force
balance velocity at early times, and the dynamics of a semipermeable inextensible membrane
resemble those of an impermeable vesicle. As the force balance velocity
decreases, the permeability velocity dominates, and the vesicle begins
to inflate to a circle with vanishing force and velocity.

\begin{figure*}[htp]
  \centering
  \ifTikz
    \input{figures/relaxationTensions.tikz}
  \else
    \includegraphics{figures/relaxationTensions.pdf}
  \fi
  \caption{\label{fig:relaxationTensions} The distribution of membrane
  tension corresponding to the relaxation dynamics in 
  Figure~\ref{fig:relaxationComposite}.}
\end{figure*}
Figure~\ref{fig:relaxationTensions} shows the tension
distribution along the relaxing membranes in
Figure~\ref{fig:relaxationComposite}. The membrane tension (color bars)
is in N/m. As the semipermeable inextensible membrane relaxes, the membrane tension
reduces in magnitude and becomes more evenly distributed along the
membrane. In the top row ($\alpha(0)=0.95$) the membrane nearly relaxes
to a circle on the right, and the membrane tension is uniform and equal
to $k_b \kappa_0^2/2$ as predicted by our analysis in
Equation~\eqref{eqn:areaROC2}. 
%In the bottom row ($\alpha(0)=0.12$), the initial vesicle shape has a
%lot of high curvature regions (and thus the low reduced area), and it
%takes more than four hours to inflate to twice the initial total water
%content for $\beta=10^{-7}$. In contrast the water enclosed inside the
%vesicle in the top row remains nearly constant in the first four hours.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Planar Shear Flow}
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \else
  \includegraphics{figures/shearComposite.pdf}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semipermeable inextensible membrane with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The equilibrium membrane shape with varying flow rates and
  membrane permeability. The red regions correspond to influx and the
  blue regions correspond to efflux The boxed membranes correspond to the
  simulation results in part (a).}
\end{figure*}

We consider a semipermeable inextensible membrane in a planar shear flow,
characterized by the elastic capillary number $Ca_\mathrm{E}=\chi\tau$ where $\tau$ is the characteristic time scale from balancing the viscous stress with the elastic stress
%in the non-dimensionalization 
(see \S~\ref{sec:formulation}) and $\chi$ is the shear rate of the
planar shear flow $\uu_{\infty}(\xx) = \chi (y,0)$.  When $\beta=0$
(impermeable case), the vesicle reduced area and fluid viscosity
contrast determine whether a vesicle tank treads or
tumbles~\cite{fin-lam-sei-gom2008, kra-win-sei-lip1996}. Focusing on
a semipermeable inextensible membrane with no viscosity contrast, 
we find that the membrane tilts to an inclination angle and undergoes
tank-treading dynamics, similar to the case of an impermeable vesicle.

In Figure~\ref{fig:shearComposite}(a), using four initial reduced areas
and two flow rates, we plot the reduced area of a semipermeable inextensible membrane
with $\beta = 10^{-3}$. As observed in a quiescent flow, the final
membrane shape is independent of the initial reduced area. However, it
does depend on the flow rate. We also observe that the amount of water
inside the vesicle remains constant until $t\sim 2$ hours, when the
normal component of the flow velocity becomes significantly smaller than
the permeable velocity, leading to a changing reduced area.

For a range of dimensionless permeability coefficient $\beta>0$ and
capillary number $Ca_\mathrm{E}$, a semipermeable inextensible membrane reaches an
equilibrium shape as in Figure~\ref{fig:shearComposite}(a). Since the
equilibrium shape depends on $Ca_\mathrm{E}$ and is independent of the
initial reduced area, we initialize the membrane with reduced area
$\alpha = 0.65$ for all simulations in
Figure~\ref{fig:shearComposite}(b), where we summarize the equilibrium
membrane shape and its reduced area. We see that the capillary number
(flow rate) significantly affects the final membrane shape, but the
permeability coefficient has a very minor effect on the equilibrium
shape for $10^{-4}\le\beta\le 10^{-2}$. Instead, $\beta$ sets the time
required for a membrane to reach its steady state configuration which is
proportional to $\beta^{-1}$, as we saw in the analysis for the
quiescent flow (\S~\ref{subsec:area_dynamics}).

%Our simulations of a semipermeable vesicle in a planar shear flow show
%that the equilibrium vesicle shape depends mostly on the capillary
%number $Ca_\mathrm{E}$, independent of the dimensionless water
%permeability $\beta$. 
The tension distribution along the equilibrium membrane shape at
$\beta=10^{-4}$ is shown in Figure~\ref{fig:shearTensions}, where the
color bars are the membrane tension in N/m. The capillary number
$Ca_\mathrm{E}$ increases from Figures~\ref{fig:shearTensions}(a)--(d),
and we observe that the tension magnitude also increases almost linearly
with $Ca_\mathrm{E}$. We also observe that the membrane tension is
relatively small at the tip when the membrane curvature is large due to
the extensional component in the shear flow.
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/shearTensions.tikz}
  \else
  \includegraphics{figures/shearTensions.pdf}
  \fi
  \caption{\label{fig:shearTensions} The tension distribution along a
  semipermeable inextensible membrane in a linear shear flow. The semipermeability constant is
  $\beta = 10^{-4}$ for all these cases, and the elastic capillary
  numbers are (a) $10^{-1}$, (b) $10^{0}$, (c), $10^{1}$, and (d)
  $10^{2}$ as in Figure~\ref{fig:shearComposite}(b).}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Poiseuille Flow}
We consider a semipermeable inextensible membrane in the Poiseuille flow $\uu =
U(1-(y/W)^2,0)$, where $U$ is the maximum velocity at $y=0$. The
non-linear effects of the Poiseuille flow on the migration of an
impermeable vesicle have been well-studied~\cite{kao-bir-mis2009}: At a
given value of the maximum velocity $U$, there exists a critical reduced
volume above which the equilibrium vesicle shape is symmetric (parachute
or bullet shapes) and the vesicle stays at $y=0$. Below this critical
reduced volume the equilibrium vesicle moves off the center and is
asymmetric (tank-treading slipper shape). We validated our numerical
codes by comparing against results in~\citet{kao-bir-mis2009} (see
\S~\ref{subsec:numerical_validation}).

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicComposite.tikz}
  \else
  \includegraphics{figures/parabolicComposite.pdf}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The equilibrium shape of
  a semipermeable inextensible membrane submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. The red regions correspond to
  influx and the blue regions correspond to efflux. (b) The steady
  state vertical displacement at four different flow velocities. The
  steady state shapes are superimposed. (c) The reduced area of the
  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The membrane
  shape shown with the background imposed flow. The channel width is
  12.5 times larger than the vesicle radius. The corresponding reduced
  area of each membrane shape is indicated by the marks in plot (c).}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicTensions.tikz}
  \else
  \includegraphics{figures/parabolicTensions.pdf}
  \fi
%  \begin{tikzpicture}[scale=1]
%    \node[inner sep=0pt] at (0,0) {
%    \includegraphics[width=\textwidth]{figures/parabolicTensions.pdf}
%    };
%    \node at (-8.2,1.5) {(a)};
%    \node at (-3.8,1.5) {(b)};
%    \node at (+0.6,1.5) {(c)};
%    \node at (+5.0,1.5) {(d)};
%  \end{tikzpicture}
  \caption{\label{fig:parabolicTensions} The equilibrium tension
  distribution of a semipermeable inextensible membrane with $\beta=10^{-3}$ in a
  parabolic flow (Figure~\ref{fig:parabolicComposite}). The flow
  velocities are (a) 200 $\mu$m/s, (b) 400 $\mu$m/s, (c) 600 $\mu$m/s,
  and (d) 800 $\mu$m/s.}
\end{figure*}
 The membrane tension distribution of the equilibrium shapes are shown
 in Figure~\ref{fig:parabolicTensions} for the flow velocities $U$ from
 $200\;\mu$m/s to $800 \;\mu$m/s. We note that in the Poiseuille flow
 the membrane tension is positive in the front, and negative in the rear
 part of the vesicle. Furthermore we also note that the tension
 magnitude is almost linearly proportional to $U$ as in the linear shear
 flow.

@@

\section{Hydrodynamics of A semipermeable inextensible membrane under strong confinement\label{sec:confinement}}
Here we consider a semipermeable inextensible membrane under strong confinement: a
long closely-fit channel and a contracting channel. In a narrow
microfluidic channel, a large pressure jump is often used to push the
vesicle through a closely-fit channel~\cite{abk-fai-sto2006}. Our
simulations show that such a configuration can lead to an amplification
of water permeation at a fast time scale of the order of mini seconds. In
addition, we find that a large value of $\beta$ is needed to keep the
membrane tension below the threshold value for membrane poration. Such
high permeability for water may be regarded as an indication that the
lipid bilayer membrane is porated under strong confinement, and our
model inextensible membrane is for a porated vesicle within the Helfrich free energy
framework. As in the previous examples, we fix the membrane length and
examine the enclosed water content as a dynamic consequence of water
flow, membrane shape deformation, and membrane tension distribution.
